Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-01-17 manuscripts/paper-1/main.tex
remove obsolete content and improve formatting

    \section{Digital twin framework}
    \label{section:framework_1}
    TODO

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Digital Twin.png}
        \caption{TODO}
        \label{todo}
    \end{figure}

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Digital Twin Deviation.png}
        \caption{TODO}
        \label{todo}
    \end{figure}

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Continuous Quality Control.png}
        \caption{TODO}
        \label{todo}
    \end{figure}

    \subsection{Real system}
    TODO

    \subsubsection{Real state (RS)}
    TODO

    \subsubsection{Real state history (RSH)}
    TODO
    \[
        RSH: \mathbb{R} \rightarrow RS
    \]

    \subsubsection{Real state transition function (RSTF)}
    TODO
    \[
        RSTF: RS \rightarrow RS
    \]

    \subsubsection{Real state prediction (RSP)}
    TODO

    \subsection{Digital twin}
    TODO

    \subsubsection{Digital state (DS)}
    TODO

    \subsubsection{Digital state history (DSH)}
    In our digital world we cannot represent the continuous time domain of the real system completely.
    Instead, we have to discretize the time domain and sample the state history function.
    \[
        RSH: \mathbb{N} \rightarrow RS
    \]

    \subsubsection{Digital state transition function (DSTF)}
    Since we do not have perfect knowledge about real state and real state transition function, our simulation models typically are non-deterministic or probabilistic.
    Here we take a probabilistic viewpoint.
    \[
        DSRF: DS \rightarrow \mathbb{P}(DS)
    \]

    \subsubsection{Digital state prediction (DSP)}
    TODO

    \section{Digital twin quality framework}
    \label{section:framework_2}
    TODO

>>>>

    \section{Our framework}
    \label{section:framework_1}
    TODO

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Digital Twin.png}
        \caption{TODO}
        \label{todo-1}
    \end{figure}

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Digital Twin Deviation.png}
        \caption{TODO}
        \label{todo-2}
    \end{figure}

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Continuous Quality Control.png}
        \caption{TODO}
        \label{todo-3}
    \end{figure}
